---
title: "Accessing RLHub Data"
author: "Henry Miller"
date: "`r doc_date()`"
vignette: >
  %\VignetteIndexEntry{Accessing RLHub Data}
  %\VignetteEngine{knitr::rmarkdown}
output: 
  BiocStyle::html_document
---

# Introduction

RLHub is the Experiment Hub for the RLSuite toolchain. It contains annotations of R-Loop consensus regions and genomic features directly relevant to R-loops, such as R-loop-forming sequencing (RLFS) and G-or-C skew regions.

All data were generated via the protocol outlined in the [RLBase-data repo](https://github.com/Bishop-Laboratory/RLBase-data). 

# Accessing RLHub Data

```{r}
library(RLHub)
```

Data can be conveniently accessed through `ExperimentHub` functions or built-in accessors available through `RLHub`.

## The data

A full manifest of the available data is found here:

```{r rlhub-types}
DT::datatable(
    read.csv(system.file("extdata", "metadata.csv", package = "RLHub")),
    options = list(
        scrollX=TRUE,
        pageLength = 5
    )
)
```
The **Tags** column list the function names used to access each data set. This method of access is detailed below.

## With built-in functions

In the below example, we show how one can access data using convenient built-in functions. The data accessed is "R-loop-binding proteins discovered from mass-spec studies."

```{r get-rlhub, message=FALSE}
rlbps <- RLHub::rlbps()
DT::datatable(rlbps)
```

As noted in the previous section, the function name is simply the value in **Tags** corresponding to the entry for that data set in the `metadata.csv` table . In this example,"rlbps" is the tag corresponding to entry \#5: "R-loop-binding proteins discovered from mass-spec studies." Therefore, the function to access this data is simply `RLHub::rlbps()`.

## With ExperimentHub Objects

```{r, message=FALSE}
library(ExperimentHub)
```

In this example, we show how to access RLHub data using the ExperimentHub object.

```{r, message=FALSE}
eh <- ExperimentHub()
rlhub <- query(eh, "RLHub")
rlhub
```

If we want to obtain the R-loop-binding proteins, for example, we can do so with the ID of that item.

```{r, message=FALSE}
rlbps <- rlhub[["EH6797"]]
DT::datatable(rlbps)
```
Finally, all package resources may be loaded as a list using `loadResources()`.

```{.r}
rlhublst <- loadResources(rlhub, package = "RLHub")
names(rlhublst) <- listResources(rlhub, package = "RLHub")
```

# Session info

<details>
<summary>Session info</summary>

```{r sessionInfo}
sessionInfo()
```

</details>
