---
title: "Accessing RLHub Data"
author:
  - name: "Henry Miller"
    affiliation: 
      - Alex Bishop Laboratory, UT Health San Antonio
      - Bioinformatics Research Network
package: RLHub
date: "`r doc_date()`"
output: 
  BiocStyle::html_document:
    toc_float: true
  BiocStyle::pdf_document: default
vignette: >
  %\VignetteIndexEntry{Accessing RLHub Data}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8} 
---

# Introduction

RLHub provides processed data sets for the RLSuite toolchain. It is an `ExperimentHub` package containing annotations of R-Loop consensus regions, genomic features directly relevant to R-loops, such as R-loop-forming sequencing (RLFS) and G-or-C skew regions, and other data of relevance to RLSuite.

All data were generated via the protocol outlined in the [RLBase-data repository](https://github.com/Bishop-Laboratory/RLBase-data). 

# Accessing RLHub Data

```{r}
library(RLHub)
```

Data can be conveniently accessed through `ExperimentHub` functions or built-in accessors available through `RLHub`.
A full manifest of the available data is found here:

```{r rlhub-types}
DT::datatable(
    read.csv(system.file("extdata", "metadata.csv", package = "RLHub")),
    options = list(
        scrollX=TRUE,
        pageLength = 5
    )
)
```
The **Tags** column list the function names used to access each data set. This method of access is detailed below.

## Built-in functions

In the below example, we show how one can access data using convenient built-in functions. 

```{r get-rlhub, message=FALSE}
# Access the R-loop binding proteins (RLBPs) data set
rlbps <- RLHub::rlbps()
DT::datatable(rlbps)
```

The data access function name is simply the value in **Tags** corresponding to the entry for that data set in the `metadata.csv` table. In this example,"rlbps" is the tag corresponding to entry \#5: "R-loop-binding proteins discovered from mass-spec studies." Therefore, the function to access this data is simply `RLHub::rlbps()`.

For examples of all accessors, please run the following:

```{.r}
?RLHub::`RLHub-package`
```

## ExperimentHub objects

```{r, message=FALSE}
library(ExperimentHub)
```

In this example, we show how to access RLHub data using the ExperimentHub object.

```{r, message=FALSE}
eh <- ExperimentHub()
rlhub <- query(eh, "RLHub")
rlhub
```

If we want to obtain the R-loop-binding proteins, for example, we can do so with the ID of that item.

```{r, message=FALSE}
rlbps <- rlhub[["EH6797"]]
DT::datatable(rlbps)
```
Finally, all package resources may be loaded as a list using `loadResources()`.

```{.r}
rlhublst <- loadResources(rlhub, package = "RLHub")
names(rlhublst) <- listResources(rlhub, package = "RLHub")
```

# Session info

```{r sessionInfo}
sessionInfo()
```
